manuscript_figures

### 2024-06-25 scripts/manuscript_figures.Rmd
updated and added temp, rate of change, kelp biomass plots

# Identify the outliers
outliers <- c(45, 37, 25, 33)

@@

# rerun model with log and without outliers
lmm_model <- lmer(log(mean_fish_biomass + 1.1) ~ log(mean_kelp_biomass + 1.1) + SITE + (1 | SITE/YEAR), data = data_clean)
#check normality
qqPlot(residuals(lmm_model)) #improved to normal

@@

@@

>>>>

# Identify the outliers
outliers <- c(45, 37, 25, 33, 37, 22)

@@

# rerun model with log and without outliers
lmm_model <- lmer(log(mean_fish_biomass + 1.1) ~ log(mean_kelp_biomass + 1.1) * YEAR + (1 | SITE), data = data_clean)
#check normality
qqPlot(residuals(lmm_model)) #improved to normal

@@

# Export to CSV file
write.csv(lmm_tidy, "output/lmm_model_results.csv", row.names = FALSE)

@@

# site not sig different
```

# Run model for fish_biomass ~ kelp_biomass * year (randomize site)
```{r}
# Fit the mixed-effects model
fit10 <- lmer(log(Fish_Biomass + 1.1) ~ log(Kelp_Biomass + 1.1) * YEAR + (1 | SITE), data = all.params.data)
summary(fit10)

# Example: Standardizing numeric variables in your dataset
all.params.data$Kelp_Biomass_standardized <- scale(all.params.data$Kelp_Biomass)
all.params.data$YEAR_standardized <- scale(all.params.data$YEAR)

# Fit the model with standardized predictors
fit10 <- lmer(log(Fish_Biomass + 1.1) ~ log(Kelp_Biomass_standardized + 1.1) * YEAR_standardized + (1 | SITE), data = all.params.data)
summary(fit10)

#view results of model
summary_text10 <- capture.output(summary(fit10))
writeLines(summary_text9, "output/model.result.tables/rugosity.not.included/summary_model_year_random.txt")
